---
title: "Welcome to Week..."
author: "Catherine Gitau"
date: "July 23, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#Tidying Data

## After this class you should be able to:
- Know what a Tidy Dataset is
- Understand the Importance of having a Tidy dataset
- Know how to Spread and Gather a dataset
- Learn how to Septerate and Unite data

## Introduction to Tidy Data | What is a Tidy Dataset? {.build}
This is data that is organised in a consistent and organised way.
We do this using the package *tidyr* which is a member of the *tidyverse* package.

```{r lib, echo = TRUE}
library(tidyverse)
```

## Different ways data can be represented
Table 1:

```{r cars, echo = TRUE}
summary(cars)
```

Table 2:

Table 3:

Table 4:

## Can you identify the data that is tidy?

##There are Rules that make a dataset tidy:
- Each Variable must have its own column
- Each observation must have its own row
- Each value Must have its own cell

#Fun Part!
## Let's try and do some computations with the data that we have

# How difficult was it to work with untidy data?

#Steps to tidying:


# Spreading and Gathering 

## Example of Spreading

## Example of Gathering

# Separating and Gathering

## Separating example

## Gathering Example


